\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2021

% ready for submission
% \usepackage{neurips_2021}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
% \usepackage[preprint]{neurips_2021}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2021}

% to avoid loading the natbib package, add option nonatbib:
\usepackage[nonatbib,preprint]{neurips_2021}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{amsmath}        % advanced math environments
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}
\lstdefinestyle{pythonstyle}{
    language=Python,
    basicstyle=\ttfamily\footnotesize,
    keywordstyle=\color{blue},
    commentstyle=\color{gray},
    stringstyle=\color{green!50!black},
    numbers=left,
    numberstyle=\tiny\color{gray},
    stepnumber=1,
    numbersep=10pt,
    backgroundcolor=\color{yellow!10},
    frame=single,
    tabsize=4,
    captionpos=b,
    breaklines=true,
    breakatwhitespace=false,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    morekeywords={self}  % Add keywords if needed
}
\lstset{style=pythonstyle}
\newcommand{\stream}[1]{\ensuremath{\mathcal{S}_{#1}}}
\newcommand{\streamty}[1]{\ensuremath{{#1}^{\omega}}}
\newcommand{\agent}{A}
\newcommand{\agentin}[1]{\ensuremath{\mathit{input}(#1)}}
\newcommand{\agentout}[1]{\ensuremath{\mathit{output}(#1)}}
\newcommand{\secref}[1]{Sec. \ref{sec:#1}}

\title{Final Paper: A Framework for Leveraging Small Language Models for Synthetic Data Generation for
Fine-Tuning}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  Zachary Grannan \\
  \And{}
  Owen Ren
}

\begin{document}

\maketitle

\begin{abstract}
Synthetic data is now commonly used in LLM post-training. However, there has
been less research into the use of domain-specific synthetic data for
fine-tuning purpose-built LLMs. In this work, we develop an agentic framework,
in the style of AgentInstruct \citep{mitra_agentinstruct_2024}, that facilitates
the generation of synthetic data for domain-specific LLM fine-tuning. Our
framework provides an API for defining agents and a declarative interface for
coordinating agents in data generation pipeline. Our framework facilitates
compositionality: for example, the caching of intermediate results in a pipeline
can be accomplished by adding a general-purpose caching agent rather than
modifying application code.  We evaluate our framework by using it to fine-tune
a model to answer questions about machine-learning papers. On a question-answer
task, our resulting fine-tuned model has performance comparable to an
alternative RAG-based approach. Our implementation, including the pipeline and scripts used
used in our evaluation is available at \url{https://github.com/zgrannan/532}. Our finetuned 
model and generated datasets are available at \url{https://huggingface.co/CPSC532}.
\end{abstract}

\input{introduction}
\input{related}
\input{methodology}
\input{pipeline}
\input{implementation}
\input{evaluation}
\input{results_analysis}
\input{conclusions}

\clearpage

\bibliographystyle{abbrvnat}
\bibliography{bib}

\input{appendix}

\end{document}
